Everything I know about Subset Sum Reconfiguration

### 2013-07-20 notes/ssr.tex
Correct label
Minor wording changes

\noindent This is a brief summary of everything I know about the subset sum reconfiguration problem as of the evening of Thursday the 18th of July.

@@

\begin{rem}
    The lower bound conjectured in Conjecture~\ref{prop:diameter} is optimal for $n<8$. I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}. An earlier version of these notes had a construction that purported to exhibit this bound, but there is an error and it does not work.
\end{rem}

>>>>

\noindent This is a brief summary of some of the things I know or conjecture about the subset sum reconfiguration problem. These are rough notes, which are likely to contain errors large and small, intended to record ideas rather than to be a polished account.

@@

\begin{rem}
    The lower bound conjectured by Conjecture~\ref{conjecture:diameter} exists and is optimal for $n<8$. I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}. An earlier version of these notes had a construction that purported to exhibit this bound, but there is an error in that construction.
\end{rem}
